Self Regulation Ontology Retest Analyses

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
expanded similar item analyses

duplicate_items = comb %>% 
  filter(grepl('dospert', V1)==FALSE) %>%
  filter(grepl('selection_optimization', V1)==FALSE) %>%
  filter(grepl('sensation_seeking', V1)==FALSE) %>%
  separate(V1, c("item1_ID", "item1_text"), sep="___") %>%
  separate(V2, c("item2_ID", "item2_text"), sep="___") %>%
  mutate(similarity = levenshteinSim(item1_text, item2_text)) %>%
  filter(similarity>0.8) %>%
  select(item1_ID, item2_ID, item1_text, item2_text)

@@

```{r}
summary(duplicate_items$t1_t1_cor)
summary(duplicate_items$t2_t2_cor)
summary(duplicate_items$t1_t2_cor)
summary(duplicate_items$t2_t1_cor)

summary(duplicate_items$t1_t1_polycor)
summary(duplicate_items$t2_t2_polycor)
summary(duplicate_items$t1_t2_polycor)
summary(duplicate_items$t2_t1_polycor)
```

>>>>

duplicate_items = comb %>% 
  filter(grepl('dospert', V1)==FALSE) %>%
  filter(grepl('selection_optimization', V1)==FALSE) %>%
  filter(grepl('sensation_seeking', V1)==FALSE) %>%
  separate(V1, c("item1_ID", "item1_text"), sep="___") %>%
  separate(V2, c("item2_ID", "item2_text"), sep="___") %>%
  mutate(similarity = levenshteinSim(item1_text, item2_text)) %>%
  filter(similarity>0.8) %>%
  select(similarity, item1_ID, item2_ID, item1_text, item2_text) %>%
  arrange(-similarity)

@@

duplicate_items %>%
  arrange(-t1_t1_polycor, -t2_t2_polycor)
```

```{r}
# summary(duplicate_items$t1_t1_cor)
# summary(duplicate_items$t2_t2_cor)
# summary(duplicate_items$t1_t2_cor)
# summary(duplicate_items$t2_t1_cor)

summary(duplicate_items$t1_t1_polycor)
summary(duplicate_items$t2_t2_polycor)
# summary(duplicate_items$t1_t2_polycor)
# summary(duplicate_items$t2_t1_polycor)
```

```{r}
tmp = duplicate_items %>%
  select(similarity, t1_t1_polycor, t2_t2_polycor) %>%
  gather(key, value, -similarity)

# tmp = duplicate_items %>%
#   select(similarity, t1_t1_polycor, t1_t2_polycor, t2_t2_polycor, t2_t1_polycor) %>%
#   gather(key, value, -similarity)

tmp %>%
  ggplot(aes(similarity, value, col=key))+
  geom_smooth(method="lm", se=FALSE)

summary(lm(value~key*similarity,tmp))
```
